\revision{Confirmation of \srcfull{} as a long period radio transient}{A new long period radio transient: Discovery of pulses repeating every 1.16 hours from \srcfull{}}

### 2025-07-14 paper/main.tex
Final changes before resubmitting

% Title of the paper, and the short title which is used in the headers.
% Keep the title short and informative.
%\title[Confirmation of \src{} as LPT]{Confirmation of \srcfull{} as a long period radio transient}
\title[1.16-hr pulses from \src{}]{\revision{Confirmation of \srcfull{} as a long period radio transient}{A new long period radio transient: Discovery of pulses repeating every 1.16 hours from \srcfull{}}}

@@

% Abstract of the paper
\begin{abstract}
We report the discovery of several new pulses from the source \srcfull{} (\src{}), originally identified from a single 2-min long pulse, confirming it as a long period transient (LPT) with a period of ${\sim}1.16\,$hours. The pulses are significantly scattered, consistent with Galactic electron density models. Two of the new pulses also had measurable polarisation, but unlike the originally detected pulse, the polarisation angle does not behave as expected from the rotating vector model. We interpret historical non-detections of \src{} as an intrinsic intermittency that occurs on month-long timescales, and discuss possible causes. We conjecture that, like some other LPTs with periods $\gtrsim 1\,$hour, \src{} \revision{is a white-dwarf binary pulsar, but note that its period is marginally shorter than the minimum known orbital period for the class of cataclysmic variables known as polars}{may host a white dwarf in a binary orbit, but note that its period is marginally shorter than the canonical orbital period minimum of cataclysmic variables}. \revision{}{Our work
highlights the importance of additional observations in establishing the nature of unusual radio-
emitting objects.}
\end{abstract}

@@

\src{}'s period and duty cycle are not dissimilar to ILT J1101+5521 and GLEAM-X J0704$-$37, \revision{which are conjectured to be on the evolutionary path towards becoming polars}{both WD + MD binary systems} (\Fig~\ref{fig:lpt_comparison}), suggesting the possibility that \src{}, too, is such a system.
Notably, its period of ${\sim}1.16\,$hours would make it shorter than the minimum known orbital period of $1.3\,$hours for \revision{confirmed}{} polars \citep{2009MNRAS.397.2170G,schwope2025polarcatcatalogpolarslowaccretion}.
This makes it an interesting test bed for the possibility that LPTs with different periods represent different stages of \revision{WD binary evolution, as they progress towards becoming polars}{WD + MD binary evolution}.
\begin{figure*}
    \centering
    \includegraphics[width=0.98\linewidth]{lpt_comparison.pdf}
    \caption{Duty cycle vs radio pulse period for various long period radio emitters \citep{deRuiter2025,2022Natur.601..526H,2023Natur.619..487H,2024NatAs...8.1159C,2005Natur.434...50H,deRuiter2025,Lee2025,2024arXiv241116606W}. The duty cycles are derived from the reported pulse widths for LPTs, which are compared to the range of the fitted, unscattered pulse widths of \src{} at 10\% of the peak. AR\,Sco \citep{2016Natur.537..374M,2018A&A...611A..66S} and other sources without well-defined duty cycles or periods \citep[e.g.][and references therein]{2021ApJ...920...45W} are not included on this plot.}
    \label{fig:lpt_comparison}
\end{figure*}

@@

\begin{figure*}
    \centering
    \includegraphics[width=0.48\linewidth]{J1755_optical.pdf}
    \includegraphics[width=0.48\linewidth]{J1755_nir.pdf}
    \caption{The $1\sigma$ positional uncertainty of \src{} derived from the MeerKAT observation taken on MJD 60602 is shown as the green ellipses overlaid on the optical (z, i, r) Panoramic Survey Telescope and Rapid Response System \citep[PanSTARRS;][]{2010SPIE.7733E..0EK,2016arXiv161205560C} image (left panel), and the infrared (K, H, J) United Kingdom Infrared Telescope Deep Sky Survey \citep[UKIDSS;][]{2007MNRAS.379.1599L} image (right panel).}
    \label{fig:localization}
\end{figure*}

>>>>

% Title of the paper, and the short title which is used in the headers.
% Keep the title short and informative.
%\title[Confirmation of \src{} as LPT]{Confirmation of \srcfull{} as a long period radio transient}
\title[1.16-hr-repeating pulses from \src{}]{\revision{Confirmation of \srcfull{} as a long period radio transient}{A new long period radio transient: Discovery of pulses repeating every 1.16 hours from \srcfull{}}}

@@

% Abstract of the paper
\begin{abstract}
We report the discovery of several new pulses from the source \srcfull{} (\src{}), originally identified from a single 2-min long pulse, confirming it as a long period transient (LPT) with a period of ${\sim}1.16\,$hours. The pulses are significantly scattered, consistent with Galactic electron density models. Two of the new pulses also had measurable polarisation, but unlike the originally detected pulse, the polarisation angle does not behave as expected from the rotating vector model. We interpret historical non-detections of \src{} as an intrinsic intermittency that occurs on month-long timescales, and discuss possible causes. We conjecture that, like some other LPTs with periods $\gtrsim 1\,$hour, \src{} \revision{is a white-dwarf binary pulsar, but note that its period is marginally shorter than the minimum known orbital period for the class of cataclysmic variables known as polars}{may host a white dwarf in a binary orbit, but note that its period is marginally shorter than the canonical orbital period minimum of cataclysmic variables}. \revision{}{Our work
highlights the importance of additional observations in establishing the nature of unusual radio-emitting objects.}
\end{abstract}

@@

\src{}'s period and duty cycle are not dissimilar to ILT J1101+5521 and GLEAM-X J0704$-$37, \revision{which are conjectured to be on the evolutionary path towards becoming polars}{both WD + MD binary systems} (\Fig~\ref{fig:lpt_comparison}), suggesting the possibility that \src{} is also such a system.
Notably, its period of ${\sim}1.16\,$hours would make it shorter than the minimum known orbital period of $1.3\,$hours for \revision{confirmed}{} polars \citep{2009MNRAS.397.2170G,schwope2025polarcatcatalogpolarslowaccretion}.
This makes it an interesting test bed for the possibility that LPTs with different periods represent different stages of \revision{WD binary evolution, as they progress towards becoming polars}{WD + MD binary evolution}.
\begin{figure*}
    \centering
    \includegraphics[width=0.98\linewidth]{lpt_comparison.pdf}
    \caption{Duty cycle vs radio pulse period for various long period radio emitters \citep{deRuiter2025,2022Natur.601..526H,2023Natur.619..487H,2024NatAs...8.1159C,2005Natur.434...50H,deRuiter2025,Lee2025,2024arXiv241116606W}. The duty cycles are derived from the reported pulse widths for LPTs, which are compared to the range of the fitted, unscattered pulse widths of \src{} at 10\% of the peak. AR\,Sco \citep{2016Natur.537..374M,2018A&A...611A..66S} and other sources without well-defined duty cycles or periods \citep[e.g.][and references therein]{2021ApJ...920...45W} are not included on this plot.}
    \label{fig:lpt_comparison}
\end{figure*}

@@

\begin{figure*}
    \centering
    \includegraphics[width=0.48\linewidth]{J1755_optical.pdf}
    \includegraphics[width=0.48\linewidth]{J1755_nir.pdf}
    \caption{The $1\sigma$ positional uncertainty of \src{} derived from the MeerKAT observation taken on MJD 60602 is shown as the green ellipses overlaid on the optical (r, i, z) Panoramic Survey Telescope and Rapid Response System \citep[PanSTARRS;][]{2010SPIE.7733E..0EK,2016arXiv161205560C} image (left panel), and the infrared (J, H, K) United Kingdom Infrared Telescope Deep Sky Survey \citep[UKIDSS;][]{2007MNRAS.379.1599L} image (right panel).}
    \label{fig:localization}
\end{figure*}
